README for Clayton Stanley's dissertation

### 2014-12-05 docs/README/readme.tex
foo

\documentclass[man,floatsintext,donotrepeattitle]{apa6}
\frenchspacing
\raggedbottom
\title{README for Clayton Stanley's dissertation}
%\shorttitle{Comparing memory models of tag retrieval}
\shorttitle{README}
\author{Clayton Stanley}
\affiliation{Rice University}
\usepackage[group-separator={,}]{siunitx}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}

@@

Run the following commands to configure the environment:

\begin{itemize}
  \item ``git clone ssh://[chil uname]@chil.rice.edu/srv/git/stanley-dissertation'':
    Clone the main repository.
  \item ``git submodule update --init --recursive'':
    Initialize and update all submodules.
    This will pull in the source data submodule.
  \item ``make -C submodules/dissertationData pull'':
    Get additional compressed source data for the source data repo.
    This includes large .csv text data extracted from the postgres tables.
    These .csv files are too large to be tracked with git.
  \item ``make -C submodules/dissertationData extract'':
    Uncompress the compressed source data.
\end{itemize}

>>>>

\documentclass[man,floatsintext,donotrepeattitle]{apa6}
\frenchspacing
\raggedbottom
\title{README for Clayton Stanley's dissertation}
%\shorttitle{Comparing memory models of tag retrieval}
\shorttitle{README}
\author{Clayton Stanley}
\affiliation{Rice University}
\usepackage[group-separator={,}]{siunitx}
\usepackage{csquotes}
\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber,doi=false,uniquename=false]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{bibliography.bib}
%\usepackage{enumitem}
\usepackage{paralist}
\usepackage[doublespacing]{setspace}
\usepackage{tocloft}

@@

First, clone the main repository:

\begin{singlespace}
\begin{compactitem}
  \item \emph{git clone ssh://[chil uname]@chil.rice.edu/srv/git/stanley-dissertation}:
    Clone the main repository.
\end{compactitem}
\end{singlespace}

Then, cd to the top level of the repository and run the following commands to configure the environment:

\begin{singlespace}
\begin{compactitem} 
  \item \emph{./check-dev-env.sh}:
    Ensures that ssh keys, hostname alias, binary dependencies, etc. are all configured properly.
    If this isn't run first, none of the following commands will work.
  \item \emph{git submodule update --init --recursive}:
    Initialize and update all submodules.
    This will pull in the source data submodule.
  \item \emph{make -C submodules/dissertationData pull}:
    Get additional compressed source data for the source data repo.
    This includes large .csv text data extracted from the postgres tables.
    These .csv files are too large to be tracked with git.
  \item \emph{make -C submodules/dissertationData extract}:
    Uncompress the compressed source data.
\end{compactitem}
\end{singlespace}

If you want this done all in one go, run the \emph{make post-clone} command at the top level of the repository:
You'll need a version of make installed to do this.
\emph{check-dev-env} checks for this binary dependency and includes a suggestion on how to install make if you don't have it.
